---
title: "Multicollinearity and variable selection in stan_glm()"
subtitle: "Using sdm package in R"
author: "Oluoch, Wyclife Agumba"
institute: "Bonn, Center for Development Research - ZEF"
date: "`r Sys.time()`"
output:
  xaringan::moon_reader:
    css: 
      - default
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "16:12"
    includes:
      after_body: [css/insert-logo.html]
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
# set default options
opts_chunk$set(echo = TRUE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, bottom, center

# An inverse slide exas

Often used for transitions

---

# A slide where bullets appear

--

* The first point goes here
```{r}
head(iris, 10) # check the first few rows
```


--

* second point
```{r}
tail(iris, 10)
```
--

* third point

---

class: center, top

# This is the one which I have included for fun `r mean(iris$Sepal.Length)`
```{r}
plot(iris$Sepal.Length ~ iris$Petal.Width)
```
--

.left[Fun]

--

.right[Funnier]

--

.center[Funniest]
